Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-28 main.tex
Started writing the algorithms for the whole navigation method

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_k}\,.
\end{equation}

@@

With the existance of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_x^3) + (2\rv{r}_{k,i}^{-1}s_xs_y^2) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_ys_x^2) + (2\rv{r}_{k,i}^{-1}s_y^3) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \alpha_{11} & \alpha_{12} \\
            \alpha_{21} & \alpha_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_x^2) \\
    \begin{split}
        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_x)\rv{y}_k \\
        &\qquad+ (4\rv{r}_{k,i}^{-1}s_xs_y)
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_y^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.

@@

% \begin{algorithm}
%     \caption{Paillier Key Generation}\label{paillier_key_gen}
%     \begin{algorithmic}[1]
%         \Procedure{PaillierKeyGen}{$security\_param$}
%         \State $p,q \gets$ \Call{GeneratePrimes}{$security\_param$}
%         \State $\lambda \gets$ \Call{lcm}{p,q}
%         \State $pk \gets (n, n+1)$
%         \State $sk \gets \lambda$
%         \State \Return $(pk, sk)$
%         \EndProcedure
%     \end{algorithmic}
% \end{algorithm}

>>>>

% Algorithm settings
\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_x^3) + (2\rv{r}_{k,i}^{-1}s_xs_y^2) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_ys_x^2) + (2\rv{r}_{k,i}^{-1}s_y^3) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \alpha_{11} & \alpha_{12} \\
            \alpha_{21} & \alpha_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_x^2) \\
    \begin{split}
        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_x)\rv{y}_k \\
        &\qquad+ (4\rv{r}_{k,i}^{-1}s_xs_y)
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_y^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.

@@

\begin{algorithm}
    \caption{Navigator Prediction Step}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$, $f$}
        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
            \State Compute $\rv{\omega}' = \mathsf{E}_{N,f,0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State $r \gets$ \Call{RandInt}{$1,N$}
            \State $\mathcal{E}_{pk}(\rv{\omega}') \gets (N+1)^{\rv{\omega}'}r^N \pmod{N^2}$
            \State Broadcast $\mathcal{E}_{pk}(\rv{\omega}')$ to sensors
        \EndFor
        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \caption{Sensor Measurement at Sensor $i$}\label{alg:measurement_info}
    \begin{algorithmic}[1]
        \Procedure{Measurement}{$i$, $s_x$, $s_y$, $r_i$, $N$, $H$, $f$}
        \State Measure $\rv{z}_{k,i}$
        \While{Navigator broadcasting}
        \State Recieve $\mathcal{E}_{pk}((\rv{x}^3_k)') = \mathcal{E}_{pk}(\mathsf{E}_{N,f,0}(\rv{x}^3_k))$
        \State Recieve remaining weights in the above form
        \EndWhile
        \For{$i = 1$ to $2$} 
            \State $\beta_i \gets $
            \State Send $\beta_i$ to navigator
        \EndFor
        \For{$i = 1$ to $2$}
            \For{$j = 1$ to $2$} 
                \State Compute $\omega' = \mathsf{E}_{N,f,0}(\omega)$ by \eqref{eqn:encode}
                \State $r \gets$ \Call{RandIntInRange}{1,N}
                \State $\mathcal{E}_{pk}(\omega') \gets (N+1)^{\omega'}r^N \pmod{N^2}$
                \State Send $\mathcal{E}_{pk}(\omega')$ to sensors
            \EndFor
        \EndFor
        \EndProcedure
    \end{algorithmic}
\end{algorithm}
